Automated Program Verification and Synthesis of Embedded \& Cyber-physical Systems: Advances and Challenges

### 2017-08-14 paper.tex
minor corrections

Generally, properties that must hold for ECPSs are related to safety/reachability and liveness. Therefore, model-checking procedures have been employed to verify those properties, even under undecidability conditions via approximations, {\it e.g.}, bounding the number of steps from initial states, which leads to bounded model checking (BMC)~\cite{Veanes09}.

@@

An efficient way to synthesize reliable ECPSs is the Counterexample Guided Inductive Synthesis (CEGIS)~\cite{David15}. Its key idea is the definition (by a user) of a set of safe states, {\it i.e.}, the specification of $\Phi$, as well as a generic template for a control system that must satisfy such a specification. The, a CEGIS engine compute values for the unknown symbols of the chosen template, which hold $\Phi$~\cite{RienerKFB16}. Abate~{\it et al.}~\cite{Abate17,abatecav2017} presented a method for synthesizing stable controllers that are suitable to continuous plants given as transfer functions~\cite{Abate17} and state-space representations~\cite{abatecav2017}, which exploits bit-accurate verification of software implemented in digital microcontrollers~\cite{Bessa16,Bessa17,dsv_spin2015}.

@@

ML techniques are already being used in the software verification area \cite{mlswverif,nguyen,bridge,babic07}. For instance, Hamel~\cite{mlswverif} proposed to induce a theory, through ML, that fits a test set for a program, in such a way that it implements the respective test set. Phuc \cite{nguyen}, in turn, applied decision tree C4.5 and multilayer perceptron to annotated programs (metrics related to structure and semantics) and tackled the generation of test sets satisfying the desired constraints. Finally, Bridge studied the automation of heuristic selection based on features, regarding first-order logic theorem proving, and Hutter {\it et. al} \cite{babic07} showed that ML can be used for improving SAT solvers regarding huge verification tasks, when applied to parameter tuning~\cite{babic07}. Given what was presented, it seems worthwhile to pursue the integration of ML to BMC-based checkers, mainly regarding solver tuning. In addition, ML can also be used for invariant computation and strengthening, which is a major bottleneck in \textit{k}-induction verification based on invariant algorithms.

>>>>

Generally, properties that must hold for ECPSs are related to safety/reachability and liveness, and the earliest works on HS and ECPS proposed approaches based on computational tree logic and linear temporal logic~\cite{Alur93}, in order to specify properties and verify those systems. In the last decade, the signal temporal logic~\cite{Maler04,Donze12} was proposed and have been used since then for this purpose, thus providing more suitable operators for dynamic systems and signal processing. Therefore, model-checking procedures have been employed to verify those properties, even under undecidability conditions via approximations, {\it e.g.}, bounding the number of steps from initial states, which leads to bounded model checking (BMC)~\cite{Veanes09}.

@@

An efficient way to synthesize reliable ECPSs is Counterexample Guided Inductive Synthesis (CEGIS)~\cite{David15}. Its key idea is the definition (by a user) of a set of safe states, {\it i.e.}, the specification of $\Phi$, as well as a generic template for a control system that must satisfy such a specification. Then, a CEGIS engine compute values for the unknown symbols of the chosen template, which hold $\Phi$~\cite{RienerKFB16}. Abate~{\it et al.}~\cite{Abate17,abatecav2017} presented a method for synthesizing stable controllers that are suitable to continuous plants given as transfer functions~\cite{Abate17} and state-space representations~\cite{abatecav2017}, which exploits bit-accurate verification of software implemented in digital microcontrollers~\cite{Bessa16,Bessa17,dsv_spin2015}, and the resulting systems must ensure non-fragile stability~\cite{Abate17} and safety~\cite{abatecav2017}. Ravanbakhsh and Sankaranarayanan~\cite{Ravanbakhsh15,Ravanbakhsh16} also employed CEGIS based on the Lyapunov's function to ensure the robust reach-while-stay property ({\it i.e.}, a safety specification)~\cite{Ravanbakhsh16} and non-zeno behavior~\cite{Ravanbakhsh15}. CEGIS was also employed to synthesize model predictive controllers for a wide varieties of applications, {\it e.g.} heating ventilation and air conditioning systems, autonomous vehicles control, and aircraft electric power system~\cite{Ghosh05,Rahman13}.

CEGIS is an important, but not the unique, example of symbolic control synthesis for ECPSs. The main advantage of using symbolic synthesis techniques ({\it e.g.}, SMT- and SAT-based) is the possibility of encoding (via logic formulae) reachability/safety specifications on original concrete systems. Indeed, there are many studies~\cite{Rungger13,AydinGol14,Holub16,Tabuada08,Zamani17,Zamani14,Zamani13,Zamani12,Alkhatib17,Lesser15,Girard13} on symbolic control synthesis for ECPS, available in literature.

A common procedure for controller synthesis for ECPS is based on finite-state approximations of infinite-states systems, {\it i.e.}, the HA. Such an approach allows the fully automated synthesis of ECPS control systems that ensure achievement of complex specifications; however, the main weakness of this approach is that it often produces complex controllers with high implementation cost. In order to avoid that problem, refined controllers have been proposed, which aim to provide some invariant properties for close-loop systems, {\it e.g.}: safety~\cite{Dallal17,Dallal13,Girard13}, reachability~\cite{Alkhatib17,Habets06}, stability~\cite{Zamani12,Tabuada08}, and safety/reachability properties, considering quantization effects~\cite{Reissig17}.

@@

ML techniques are already being used in the software verification area \cite{mlswverif,nguyen,bridge,babic07}. For instance, Hamel~\cite{mlswverif} proposed to induce a theory, through ML, that fits a test set for a program, in such a way that it implements the respective test set. Phuc \cite{nguyen}, in turn, applied decision tree C4.5 and multilayer perceptron to annotated programs (metrics related to structure and semantics) and tackled the generation of test sets satisfying the desired constraints. Bridge studied the automation of heuristic selection based on features, regarding first-order logic theorem proving, and Hutter {\it et. al} \cite{babic07} showed that ML can be used for improving SAT solvers regarding huge verification tasks, when applied to parameter tuning~\cite{babic07}. Seshia {\it et al.}~\cite{Seshia17}, in turn, showed that control syntheses based on ML is also a trend, since it has been applied to different applications and model classes~\cite{Jha10,Sadigh14}. Finally, ML can also be used for invariant computation and strengthening, which is a major bottleneck in \textit{k}-induction verification based on invariant algorithms. As a consequence of what was presented, it seems worthwhile to pursue integration of ML into BMC-based checkers, given that it has the potential to tackle many open problems or at least enhance existing solutions.
